Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-09-27 index.qmd
add updates

  write.csv(total, "Data/Resampled_saved_data_total.csv", row.names = F)
}

# reframing <- total %>% 
#   group_by(true_fct) %>% 
#   dplyr::filter(res == 10) %>% 
#   ungroup() %>% 
#   mutate(diff = max(prop)-prop) %>% 
#   dplyr::select(true_fct,diff)
#   
# 
# total <- total %>% 
#   left_join(reframing, by = "true_fct") %>% 
#   mutate(prop = prop + diff) %>% 
#   dplyr::select(-diff)

@@

(plot <- ggplot(NewData)+
  geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 
                  color = true_fct, group = true_fct, fill = true_fct
                  ), alpha = 0.2)+
  geom_line(aes(x = sqrt(area), y = fit,
                color = true_fct, group = true_fct
                ))+
      scale_fill_manual(name = NULL,
                        values = cols_fill,
                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
    scale_color_manual(name = NULL,
                      values = cols_fill,
                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
  theme_Bede()+
  xlab("Resolution (m)") +
  ylab("Agreement")+
  theme(axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.key.size = unit(1, "cm")
          )

>>>>

  write.csv(total, "Data/Resampled_saved_data_total.csv", row.names = F)

# reframing <- total %>% 
#   group_by(true_fct) %>% 
#   dplyr::filter(res == 10) %>% 
#   ungroup() %>% 
#   mutate(diff = max(prop)-prop) %>% 
#   dplyr::select(true_fct,diff)

# total <- total %>% 
#   left_join(reframing, by = "true_fct") %>% 
#   mutate(prop = prop + diff) %>% 
#   dplyr::select(-diff)
 # validation <- read.csv( "Data/Resampled_saved_data.csv")

@@

(plot <-   NewData  %>% 
  dplyr::filter(true_fct != 1,
                true_fct != 6,
                true_fct != 7,
                true_fct != 8) %>%
ggplot()+
  geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 
                  color = true_fct, group = true_fct, fill = true_fct
                  ), alpha = 0.2)+
  geom_line(aes(x = sqrt(area), y = fit,
                color = true_fct, group = true_fct
                ))+
      scale_fill_manual(name = NULL,
                        values = cols_fill,
                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
    scale_color_manual(name = NULL,
                      values = cols_fill,
                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
  theme_Bede()+
  xlab("Resolution (m)") +
  ylab("Agreement")+
  theme(axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.key.size = unit(1, "cm")
          )
